    \section{Introduction}

    Shape optimization is inherently an infinite-dimensional problem,
    for which tractable formulations are of particular interest.
    It appears in a range of problems in aerospace design, and most notably
    aerostructural optimization which has been the bread-and-butter of the \gls{mdo} field.

    These is very little literature, if any, on solid rocket conceptual design,
    for several reasons. (1) The physics governing internal reactive flow is extremely complex,
    and there are no open-source tools that don't require domain knowledge and
    can efficiently simulate such a scenario.
    (2) There are few entities that design and build solid rocket motors, and since they have
    large amounts of resources and time and little competition there has been no impetus
    improve solid rocket design methods. (3) Solid rocket motors are relatively limited
    in capability because their burn rate is almost completely uncontrollable other
    than by properly designing the internal geometry of the rocket or actuating the
    throat of the nozzle. For this reason liquid propellant rockets have been preferred for
    many applications. (4) Rocket design is often proprietary due to arms regulations.

    This is an interesting problem where a \gls{sdp} for geometry design,
    coupled with first-order flow models may offer a good alternative to
    more traditional gradient-based methods which are used alongside
    high-fidelity internal flow simulations.
    Furthermore, problems of the form I pose appear in other interesting
    aerospace problems, such as hypersonic vehicle external geometry design,
    so the formulation has valuable extensions.
